Title Goes Here

### 2020-04-17 analysis/paper/paper.Rmd
add more plots

@@

fviz_pca_var(SYG_1xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))
```

@@

fviz_pca_var(SYG_4xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))
```

>>>>

SYG6_PC1_v <- fviz_contrib(SYG6_xx_pca, choice = "var", axes = 1, top = 7)
SYG6_PC2_v <- fviz_contrib(SYG6_xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(SYG6_PC1_v, SYG6_PC2_v, nrow =1)

@@

fviz_pca_var(SYG_1xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

SYG_1PC1_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 1, top = 7)
SYG_1PC2_v <- fviz_contrib(SYG_1xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(SYG_1PC1_v, SYG_1PC2_v, nrow =1)

@@

fviz_pca_var(SYG_4xx_pca, col.var = "contrib",
             gradient.cols = c("#00AFBB", "#E7B800", "#FC4E07"))

SYG_4PC1_v <- fviz_contrib(SYG_4xx_pca, choice = "var", axes = 1, top = 7)
SYG_4PC2_v <- fviz_contrib(SYG_4xx_pca, choice = "var", axes = 2, top = 7)

grid.arrange(SYG_4PC1_v, SYG_4PC2_v, nrow =1)
```
